Does freshwater connectivity influence phosphorus retention in lakes?

### 2019-01-20 manuscript/manuscript.Rmd
fight with docker

liftr:
  maintainer: "Joseph Stachelek"
  email: "stachel2@msu.edu"
  from: "rocker/geospatial:latest"
  pandoc: false
  texlive: true
  sysdeps:
    - grass
    - p7zip-full
  cran:
    - LAGOSNE
    - brms
    - dplyr
    - tidyr
    - modelr
    - data.tree
    - ggplot2
    - tidybayes
    - cowplot
    - nesRdata
    - partykit
    - ggridges
    - pinp
  remotes:
    - "jsta/nhdR"
    - "jsta/spnetwork"
    - "jsta/streamnet"
    - "jsta/rgrass7sf"

>>>>

liftr:
  maintainer: "Joseph Stachelek"
  email: "stachel2@msu.edu"
  from: "rocker/geospatial:latest"
  pandoc: false
  texlive: true
  sysdeps:
    - grass-dev
    - p7zip-full
    - curl
    - texlive-base
    - texlive-extra-utils 
  cran:
    - LAGOSNE
    - brms
    - dplyr
    - tidyr
    - modelr
    - data.tree
    - ggplot2
    - tidybayes
    - cowplot
    - nesRdata
    - partykit
    - ggridges
    - pinp
  remotes:
    - "jsta/nhdR"
    - "jsta/spnetwork"
    - "jsta/streamnet"
    - "jsta/rgrass7sf"
